Plug-and-play dual-tree algorithm runtime analysis

### 2015-10-07 bounds-files/conclusion.tex
Word change suggestion from Pari.

Our main result, Theorem \ref{thm:ct-runtime}, allows plug-and-play runtime
bounding of these algorithms.  We have shown that Theorem \ref{thm:ct-runtime}
is useful for bounding the runtime of nearest neighbor search (Theorem
\ref{thm:nns}), approximate kernel density estimation (Theorem
\ref{thm:kde-bound}), exact range count, and exact range search (Theorem
\ref{thm:rs}).  With our contribution, bounding a cover tree dual-tree algorithm
is straightforward and only involves bounding the maximum size of the reference
set, $| R^* |$.

>>>>

Our main result, Theorem \ref{thm:ct-runtime}, allows plug-and-play runtime
bounding of these algorithms.  We have shown that Theorem \ref{thm:ct-runtime}
is useful for bounding the runtime of nearest neighbor search (Theorem
\ref{thm:nns}), approximate kernel density estimation (Theorem
\ref{thm:kde-bound}), exact range count, and exact range search (Theorem
\ref{thm:rs}).  With our contribution, bounding a cover tree dual-tree algorithm
is streamlined and only involves bounding the maximum size of the reference
set, $| R^* |$.
